---
title: "'The Naked Emperor'- thesis syntax 1: Make Siena Objects & QAP"
subtitle: "Lisanne van Veen"
output: pdf_document
---

The script creates Siena objects for the classrooms containing the following variables:

Dependent variable: Naked emperor network
Dyadic covariates: relational aggression, perceived antisocial behavior, social behavior, gossip target, friends and antipathy
Varying covariates: indegrees of friends (sociometric popularity)
Constant covariate: Gender

To do this yourself:
Download the RECENS DATASET and change the path, so it leads to the folders that contain the network data (named "Wave1" till "Wave4").
Further down, the path to the student data must then also be changed.

This script also performs a QAP analysis for the networks of status discrepancy and the Naked emperor network. It also creates  list including all the relevant variables for the class, to be used for the descriptives.

### preliminaries

```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r libraries}
# load libraries
library(tidyverse)
library(dplyr)
library(sna)
library(igraph)
library(haven)
library(multinet)
library(RSiena)
```

```{r define school and classroom}
school <-1000         # change to relevant school number
classroom <-1200      # change to relevant school id
path <- "/Users/lisanne/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/"
```

### functions

```{r cleanNet function to quickly clean the network}
cleanNet <- function(x){
students <- x %>% select("X0") # 1st col from csv load contains student numbers
NE <- x %>% select(-"X0") # remove this from df
NE <- as.matrix(NE) # transform into matrix
rownames(NE) <- colnames(NE)<- students[[1]] #give student numbers as row and colnames
return(NE)
}
```

```{r impute missings}
# input is network of interest and earlier wave + vector with numbers of students absent during the survey
missingImpute <- function(Source,Target,abs){
    n1 <- Source # earlier wave
    n2 <- Target # wave of interest
    n2[rownames(n2) %in% abs & rownames(n2) %in% rownames(n1), colnames(n2) %in% colnames(n1)] <- n1[rownames(n1) %in% abs, colnames(n1) %in% colnames(n2)] # insert values of former wave in current wave, for absent students (nominations for those also present in the former network)
    n2[is.na(n2)] <- 0 # if any NA left, replace with 0
    diag(n2) <- 0 # diag = 0
    return(n2)
}
```

### load data

```{r 1st wave status networks}
# The data is loaded and directly cleaned and presented as defined by the cleanNet function
# Wave 1
seconddegree_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/25/",classroom,"_25_1.csv")))
firstdegree_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/24/",classroom,"_24_2.csv")))
emperor_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/24/",classroom,"_24_13.csv")))
```

```{r 2nd wave status networks}
# Wave 2
seconddegree_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/23/",classroom,"_23_1_2h.csv")))
firstdegree_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/22/",classroom,"_22_1_2h.csv")))
emperor_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/23/",classroom,"_23_4_2h.csv")))
```

```{r 3rd wave status networks}
# Wave 3
seconddegree_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/22/",classroom,"_22_1_3h.csv")))
firstdegree_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/21/",classroom,"_21_1_3h.csv")))
emperor_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/22/",classroom,"_22_4_3h.csv")))
```

```{r 4rd wave status networks}
# Wave 4
seconddegree_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/37/",classroom,"_37_1_4h.csv")))
firstdegree_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/27/",classroom,"_27_1_4h.csv")))
emperor_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/37/",classroom,"_37_4_4h.csv")))
```

```{r}
# load affective data
aff_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/15/",classroom,"_15_1.csv")))
aff_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/11/",classroom,"_11_2h.csv")))
aff_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/19/",classroom,"_19_3h.csv")))
aff_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/20/",classroom,"_20_4h.csv")))
```

```{r}
# Wave 1 (not used in analysis, however to have data for missing values)
# RELATIONAL AGGRESSION
overt_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/33/",classroom,"_33_2.csv")))
gossips_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/33/",classroom,"_33_4.csv")))
mocks_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/33/",classroom,"_33_6.csv")))
humiliate_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/33/",classroom,"_33_8.csv")))

# PERCEIVED ANTISOCIAL BEHAVIOR
gossipy_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/23/",classroom,"_23_4.csv")))
fights_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/23/",classroom,"_23_2.csv")))

# PERCEIVED SOCIAL BEHAVIOR
kind_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/23/",classroom,"_23_5.csv")))
protects_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/24/",classroom,"_24_8.csv")))
solvedispute_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/24/",classroom,"_24_10.csv")))
trust_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/24/",classroom,"_24_9.csv")))
helps_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/24/",classroom,"_24_12.csv")))
```

```{r 2nd wave bullying networks}
# Wave 2
# Relational aggression
overt_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/32/",classroom,"_32_2_2h.csv")))
gossips_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/32/",classroom,"_32_4_2h.csv")))
mocks_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/32/",classroom,"_32_6_2h.csv")))
humiliate_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/32/",classroom,"_32_8_2h.csv")))

# Antisocial behavior
gossipy_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/21/",classroom,"_21_4_2h.csv")))
fights_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/21/",classroom,"_21_2_2h.csv")))

# social behavior
kind_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/21/",classroom,"_21_5_2h.csv")))
protects_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/22/",classroom,"_22_8_2h.csv")))
solvedispute_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/22/",classroom,"_22_10_2h.csv")))
trust_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/22/",classroom,"_22_9_2h.csv")))
helps_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/22/",classroom,"_22_12_2h.csv")))
```

```{r 3rd wave bullying networks}
# Wave 3
# Relational aggression
overt_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/39/",classroom,"_39_2_3h.csv")))
gossips_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/39/",classroom,"_39_4_3h.csv")))
mocks_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/39/",classroom,"_39_6_3h.csv")))
humiliate_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/39/",classroom,"_39_8_3h.csv")))

# antisocial behavior
gossipy_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/20/",classroom,"_20_4_3h.csv")))
fights_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/20/",classroom,"_20_2_3h.csv")))

# social behavior
kind_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/20/",classroom,"_20_5_3h.csv")))
protects_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/21/",classroom,"_21_6_3h.csv")))
solvedispute_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/21/",classroom,"_21_8_3h.csv")))
trust_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/21/",classroom,"_21_7_3h.csv")))
helps_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/21/",classroom,"_21_10_3h.csv")))
```

```{r 4th wave bullying networks}
# Wave 4
# Relational aggression
overt_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/38/",classroom,"_38_2_4h.csv")))
gossips_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/38/",classroom,"_38_4_4h.csv")))
mocks_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/38/",classroom,"_38_6_4h.csv")))
humiliate_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/38/",classroom,"_38_8_4h.csv")))

# antisocial behavior
gossipy_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/26/",classroom,"_26_4_4h.csv")))
fights_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/26/",classroom,"_26_2_4h.csv")))

# social behavior
kind_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/26/",classroom,"_26_5_4h.csv")))
protects_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/27/",classroom,"_27_6_4h.csv")))
solvedispute_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/27/",classroom,"_27_8_4h.csv")))
trust_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/27/",classroom,"_27_7_4h.csv")))
helps_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/27/",classroom,"_27_10_4h.csv")))
```

```{r}
# Gossip about
gossiptarget_1 <- cleanNet(read.csv(paste0(path,"Wave1/",school,"/", classroom,"/33/",classroom,"_33_3.csv")))
gossiptarget_2 <- cleanNet(read.csv(paste0(path,"Wave2/",school,"/", classroom,"/32/",classroom,"_32_3_2h.csv")))
gossiptarget_3 <- cleanNet(read.csv(paste0(path,"Wave3/",school,"/", classroom,"/39/",classroom,"_39_3_3h.csv")))
gossiptarget_4 <- cleanNet(read.csv(paste0(path,"Wave4/",school,"/", classroom,"/38/",classroom,"_38_3_4h.csv")))
```

### network dichotomizing / merging

```{r firstwave seconddegree network}
seconddegree_1[seconddegree_1 %in% c(-1,-2)] <- 0
seconddegree_1[seconddegree_1 %in% c(1,2)] <- 1
```

```{r, affective networks}
friends_1 <- ifelse(aff_1 == 2, 1, 0)
friends_2 <- ifelse(aff_2 == 2, 1, 0)
friends_3 <- ifelse(aff_3 == 2, 1, 0)
friends_4 <- ifelse(aff_4 == 2, 1, 0)

dislike_1 <- ifelse(aff_1 == -2 | aff_1 == -1, 1, 0)
dislike_2 <- ifelse(aff_2 == -2 | aff_2 == -1, 1, 0)
dislike_3 <- ifelse(aff_3 == -2 | aff_3 == -1, 1, 0)
dislike_4 <- ifelse(aff_4 == -2 | aff_4 == -1, 1, 0)
```

```{r}
# merge networks to one without dichotomizing
relational_1 <- gossips_1 + mocks_1 + humiliate_1 + overt_1
antisocial_1 <- gossipy_1+fights_1
social_1 <- kind_1 + protects_1 + solvedispute_1 + trust_1 + helps_1

relational_2 <- gossips_2 + mocks_2 + humiliate_2 + overt_2
antisocial_2 <- gossipy_2+fights_2
social_2 <- kind_2 + protects_2 + solvedispute_2 + trust_2 + helps_2

relational_3 <- gossips_3 + mocks_3 + humiliate_3 + overt_3
antisocial_3 <- gossipy_3+fights_3
social_3 <- kind_3 + protects_3 + solvedispute_3 + trust_3 + helps_3

relational_4 <- gossips_4 + mocks_4 + humiliate_4 + overt_4
antisocial_4 <- gossipy_4+fights_4
social_4 <- kind_4 + protects_4 + solvedispute_4 + trust_4 + helps_4
```

### select student belonging to the class at last 3 waves

```{r load student data in dataframe}
student_data <- as_tibble(read_sav("/Users/lisanne/Desktop/Master Computational Social Science/NETWORK PAPER/OTKA_dataset/ENG - Data/OTKA_student_w1234.sav"))
```

```{r}
# filter on student numbers that exist throughout the last 2 waves
studdata <- student_data %>% filter(class_2 == classroom & class_3 == classroom & class_4 == classroom) 
stud <- studdata$idcode
```

```{r select students present in all waves}
seconddegree_1 <- seconddegree_1[rownames(seconddegree_1) %in% stud,colnames(seconddegree_1) %in% stud] 
firstdegree_1 <- firstdegree_1[rownames(firstdegree_1) %in% stud,colnames(firstdegree_1) %in% stud]
emperor_1 <- emperor_1[rownames(emperor_1) %in% stud,colnames(emperor_1) %in% stud]

seconddegree_2 <- seconddegree_2[rownames(seconddegree_2) %in% stud,colnames(seconddegree_2) %in% stud] 
firstdegree_2 <- firstdegree_2[rownames(firstdegree_2) %in% stud,colnames(firstdegree_2) %in% stud]
emperor_2 <- emperor_2[rownames(emperor_2) %in% stud,colnames(emperor_2) %in% stud]

seconddegree_3 <- seconddegree_3[rownames(seconddegree_3) %in% stud,colnames(seconddegree_3) %in% stud] 
firstdegree_3 <- firstdegree_3[rownames(firstdegree_3) %in% stud,colnames(firstdegree_3) %in% stud]
emperor_3 <- emperor_3[rownames(emperor_3) %in% stud,colnames(emperor_3) %in% stud]

seconddegree_4 <- seconddegree_4[rownames(seconddegree_4) %in% stud,colnames(seconddegree_4) %in% stud] 
firstdegree_4 <- firstdegree_4[rownames(firstdegree_4) %in% stud,colnames(firstdegree_4) %in% stud]
emperor_4 <- emperor_4[rownames(emperor_4) %in% stud,colnames(emperor_4) %in% stud]
```

```{r}
friends_1 <- friends_1[rownames(friends_1) %in% stud,colnames(friends_1) %in% stud]
friends_2 <- friends_2[rownames(friends_2) %in% stud,colnames(friends_2) %in% stud]
friends_3 <- friends_3[rownames(friends_3) %in% stud,colnames(friends_3) %in% stud]
friends_4 <- friends_4[rownames(friends_4) %in% stud,colnames(friends_4) %in% stud]

dislike_1 <- dislike_1[rownames(dislike_1) %in% stud,colnames(dislike_1) %in% stud]
dislike_2 <- dislike_2[rownames(dislike_2) %in% stud,colnames(dislike_2) %in% stud]
dislike_3 <- dislike_3[rownames(dislike_3) %in% stud,colnames(dislike_3) %in% stud]
dislike_4 <- dislike_4[rownames(dislike_4) %in% stud,colnames(dislike_4) %in% stud]
```

```{r}
relational_1 <- relational_1[rownames(relational_1) %in% stud,colnames(relational_1) %in% stud]
relational_2 <- relational_2[rownames(relational_2) %in% stud,colnames(relational_2) %in% stud]
relational_3 <- relational_3[rownames(relational_3) %in% stud,colnames(relational_3) %in% stud]
relational_4 <- relational_4[rownames(relational_4) %in% stud,colnames(relational_4) %in% stud]

antisocial_1 <- antisocial_1[rownames(antisocial_1) %in% stud,colnames(antisocial_1) %in% stud]
antisocial_2 <- antisocial_2[rownames(antisocial_2) %in% stud,colnames(antisocial_2) %in% stud]
antisocial_3 <- antisocial_3[rownames(antisocial_3) %in% stud,colnames(antisocial_3) %in% stud]
antisocial_4 <- antisocial_4[rownames(antisocial_4) %in% stud,colnames(antisocial_4) %in% stud]

social_1 <- social_1[rownames(social_1) %in% stud,colnames(social_1) %in% stud]
social_2 <- social_2[rownames(social_2) %in% stud,colnames(social_2) %in% stud]
social_3 <- social_3[rownames(social_3) %in% stud,colnames(social_3) %in% stud]
social_4 <- social_4[rownames(social_4) %in% stud,colnames(social_4) %in% stud]
```

```{r}
gossiptarget_1 <- gossiptarget_1[rownames(gossiptarget_1) %in% stud,colnames(gossiptarget_1) %in% stud] 
gossiptarget_2 <- gossiptarget_2[rownames(gossiptarget_2) %in% stud,colnames(gossiptarget_2) %in% stud] 
gossiptarget_3 <- gossiptarget_3[rownames(gossiptarget_3) %in% stud,colnames(gossiptarget_3) %in% stud] 
gossiptarget_4 <- gossiptarget_4[rownames(gossiptarget_4) %in% stud,colnames(gossiptarget_4) %in% stud] 
```

# missings
```{r}
# which students were not present during the survey?
abs.1 <- studdata %>% filter(participate1 == 0) %>% select(idcode)
abs.2 <- studdata %>% filter(participate2 == 0) %>% select(idcode)
abs.3 <- studdata %>% filter(participate3 == 0) %>% select(idcode)
abs.4 <- studdata %>% filter(participate4 == 0) %>% select(idcode)
```

# imputation

```{r}
emperor_2 <- missingImpute(emperor_1, emperor_2, abs.2$idcode)
emperor_3 <- missingImpute(emperor_2, emperor_3, abs.3$idcode)
emperor_4 <- missingImpute(emperor_3, emperor_4, abs.4$idcode)
```

```{r}
firstdegree_2 <- missingImpute(firstdegree_1, firstdegree_2, abs.2$idcode)
firstdegree_3 <- missingImpute(firstdegree_2, firstdegree_3, abs.3$idcode)
firstdegree_4 <- missingImpute(firstdegree_3, firstdegree_4, abs.4$idcode)
```

```{r}
seconddegree_2 <- missingImpute(seconddegree_1, seconddegree_2, abs.2$idcode)
seconddegree_3 <- missingImpute(seconddegree_2, seconddegree_3, abs.3$idcode)
seconddegree_4 <- missingImpute(seconddegree_3, seconddegree_4, abs.4$idcode)
```

```{r}
friends_2 <- missingImpute(friends_1, friends_2, abs.2$idcode)
friends_3 <- missingImpute(friends_2, friends_3, abs.3$idcode)
friends_4 <- missingImpute(friends_3, friends_4, abs.4$idcode)
```

```{r}
dislike_2 <- missingImpute(dislike_1, dislike_2, abs.2$idcode)
dislike_3 <- missingImpute(dislike_2, dislike_3, abs.3$idcode)
dislike_4 <- missingImpute(dislike_3, dislike_4, abs.4$idcode)
```

```{r}
relational_2 <- missingImpute(relational_1, relational_2, abs.2$idcode)
relational_3 <- missingImpute(relational_2, relational_3, abs.3$idcode)
relational_4 <- missingImpute(relational_3, relational_4, abs.4$idcode)

antisocial_2 <- missingImpute(antisocial_1, antisocial_2, abs.2$idcode)
antisocial_3 <- missingImpute(antisocial_2, antisocial_3, abs.3$idcode)
antisocial_4 <- missingImpute(antisocial_3, antisocial_4, abs.4$idcode)

social_2 <- missingImpute(social_1, social_2, abs.2$idcode)
social_3 <- missingImpute(social_2, social_3, abs.3$idcode)
social_4 <- missingImpute(social_3, social_4, abs.4$idcode)

gossiptarget_2 <- missingImpute(gossiptarget_1, gossiptarget_2, abs.2$idcode)
gossiptarget_3 <- missingImpute(gossiptarget_2, gossiptarget_3, abs.3$idcode)
gossiptarget_4 <- missingImpute(gossiptarget_3, gossiptarget_4, abs.4$idcode)
```

# adjecency matrix (needed for variables that depend on indegrees)

```{r}
friends_2_adj <- graph.adjacency(friends_2, mode = "directed")
friends_3_adj <- graph.adjacency(friends_3, mode = "directed")
friends_4_adj <- graph.adjacency(friends_4, mode = "directed")
```

# make Siena objects

```{r, message = F}
# define number of actors
numberActors <- nrow(emperor_2)
```

```{r}
# DEFINE DEPENDENT NETWORK VARIABLES
emperors <- sienaDependent(array(
    c(emperor_2,emperor_3,emperor_4),
    dim = c(numberActors,numberActors,3)),allowOnly = F) # remove restriction to use siena08 and multigroup analysis later
```

```{r}
# PREDICTOR NETWORKS (time-varying dyadic relationships):
relational <- varDyadCovar(array(c(relational_2,relational_3),
	dim=c(numberActors,numberActors,2)))

antisocial <- varDyadCovar(array(c(antisocial_2,antisocial_3),
	dim=c(numberActors,numberActors,2)))

social <- varDyadCovar(array(c(social_2,social_3),
	dim=c(numberActors,numberActors,2)))

gossiptarget <- varDyadCovar(array(c(gossiptarget_2,gossiptarget_3),
	dim=c(numberActors,numberActors,2)))

friends <- varDyadCovar(array(c(friends_2,friends_3),
	dim=c(numberActors,numberActors,2)))

antipathy <- varDyadCovar(array(
    c(dislike_2,dislike_3,dislike_4),
    dim = c(numberActors,numberActors,2))) 
```

```{r}
# VARIANT ACTOR ATTRIBUTE:
# indegree of friendship
n_friends<- cbind(degree(friends_2_adj, mode = "in"),degree(friends_3_adj, mode = "in"),degree(friends_4_adj, mode = "in"))

# Normalize
n_friends <- (n_friends/max(n_friends))*10

# independent variables should not have much more than 10 categories
n_friends[n_friends > 0 & n_friends <= 1] <- 1
n_friends[n_friends > 1 & n_friends <= 2] <- 2
n_friends[n_friends > 2 & n_friends <= 3] <- 3
n_friends[n_friends > 3 & n_friends <= 4] <- 4
n_friends[n_friends > 4 & n_friends <= 5] <- 5
n_friends[n_friends > 5 & n_friends <= 6] <- 6
n_friends[n_friends > 6 & n_friends <= 7] <- 7
n_friends[n_friends > 7 & n_friends <= 8] <- 8
n_friends[n_friends > 8 & n_friends <= 9] <- 9
n_friends[n_friends > 9 & n_friends <= 10] <- 10
nfriends <- varCovar(n_friends)
```

```{r}
# Constant actor variable
Gender <- as.numeric(studdata$gender_2)
Gender <- coCovar(Gender, centered = F)
```

### Save object
```{r}
# For MoM analysis siena07 siena08, multigroup siena07 and sienaBayes.
netDynamics <- sienaDataCreate(emperors, relational, antisocial, social, gossiptarget, friends, antipathy, nfriends, Gender)
save(netDynamics, file=paste0('netDynamics',classroom,'.Rdata'))
```

# QAP-test

### QAP Naked Emperors and Upward Status Discrepancy networks 

```{r}
### COMPARING NAKED EMPEROR AND 1st degree 2nd degree discrepancy
# 2 - 1
# 2nd wave
discrepancy_2 <- seconddegree_2 - firstdegree_2 # others look up nominations - I look up nominations = 1 (discrepancy), 0 (equal) or -1 looked up to but not by others
discrepancy_2[discrepancy_2 == -1] = 0 # remove -1 to only keep discrepancy nominations
discrepancy_2_adj <- graph.adjacency(discrepancy_2, mode = "directed")

# 2 - 1
# 3d wave
discrepancy_3 <- seconddegree_3 - firstdegree_3 # others look up nominations - I look up nominations = 1 (discrepancy), 0 (equal) or -1 looked up to but not by others
discrepancy_3[discrepancy_3 == -1] = 0 # remove -1 to only keep discrepancy nominations
discrepancy_3_adj <- graph.adjacency(discrepancy_3, mode = "directed")

# 2 - 1
# 4th wave
discrepancy_4 <- seconddegree_4 - firstdegree_4 # others look up nominations - I look up nominations = 1 (discrepancy), 0 (equal) or -1 looked up to but not by others
discrepancy_4[discrepancy_4 == -1] = 0 # remove -1 to only keep discrepancy nominations
discrepancy_4_adj <- graph.adjacency(discrepancy_4, mode = "directed")
```

```{r}
# QAP analysis using netlm, for each status discrepancy network and NE network. 
qap2  <-netlm(y=discrepancy_2,x=emperor_2,nullhyp=c("qap"), test.statistic=c("t-value"))

qap3 <- netlm(y=discrepancy_3,x=emperor_3,nullhyp=c("qap"), test.statistic=c("t-value"))

qap4 <- netlm(y=discrepancy_4,x=emperor_4,nullhyp=c("qap"), test.statistic=c("t-value"))
```

### Save results qap-test
```{r}
save(qap2, file = paste0("qap2",classroom,".Rdata"))
save(qap3, file = paste0("qap3",classroom,".Rdata"))
save(qap4, file = paste0("qap4",classroom,".Rdata"))
```

### Create list with all variables

```{r}
variablelist <-list(list(emperor_2,emperor_3,emperor_4),list(relational_2,relational_3,relational_4),list(antisocial_2,antisocial_3,antisocial_4),list(social_2,social_3,social_4),list(gossiptarget_2,gossiptarget_3,gossiptarget_4),list(friends_2,friends_3,friends_4),list(dislike_2,dislike_3,dislike_4),n_friends,studdata$gender_2)

names(variablelist) <- c("emperors","relational","antisocial","social","gossip","friendship","antipathy","n_friends","gender")


save(variablelist, file = paste0("variables_",classroom,".Rdata"))
```
