---
title: "'The Naked Emperor'- thesis syntax 3: Analysis Model 1 - SAOM MoM and meta-analysis"
subtitle: "Lisanne van Veen"
output: pdf_document
---
This script Runs the first model (structural effects + gender effects) in R for Method of Moments for each class, followed by meta-analysis of the results.

Algorithmic parameters are adapted to each classroom for reaching convergence.
After a first round, effects with high standard errors are set to fixed values for more reliable estimates for other model effects.
Goodness of Fit is assessed for indegrees, outdegrees, triadic closure and geodesic distribution.

### preliminaries
```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r}
library(RSiena)
library(tidyverse)
library(kableExtra)
```

### functions

```{r}
makeData <- function(i){ # setting: default, dolby = F

  load(paste0('netDynamics',i,'.Rdata')) # load data
  dataset <- netDynamics
  effects <- getEffects(dataset) # get effects
  
  # structural effects
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  
  # gender effects
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  
  # 2 algorithms:
  # for the first run, and repeated runs if necessary (after max convergence > 0.5)
  # n3=5000 for publication
  
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = F, seed=567)
  
  # for other repeated runs if necessary (after 0.2 < max conv. < 0.5)
   # n2start 2.52*(p+7) where p is number of parameters-conditional rate functions (Manual, p.79)
  # high value is double
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678)
  
  # output is a list including the data, the effects, and two algorithms
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
# Utility function: variation of a siena07 function,
# For repeated runs of siena07 until convergence is reached or deemed unfeasible
siena07ToConvergence <- function(alg0, alg1, dat, eff, ans0=NULL, ...){
  numr <- 0 # count number of runs
  ans <- siena07(x = alg0, data=dat, effects=eff, prevAns=ans0, returnDeps= T,...) # first run
  
  repeat { # code will be repeated until certain conditions are satisfied
    
    save(ans, file=paste("ans1",numr,".RData",sep="")) # save first run results as R object, to be safe
    numr <- numr+1 # count number of repeated runs
    tm <- ans$tconv.max # maximum convergence indicator
    cat(numr, tm,"\n") # report progress
    
    # Stop if:
    if (tm < 0.20) {break} # run is sufficiently successful
    if (tm > 10) {break}   # there is no hope for good estimates
    if (numr > 10) {break} # it takes too many runs for convergence
    
    # Continue if
    if (tm > 0.5){ # max convergence is above 0.5
      ans <- siena07(alg0, data=dat, effects=eff, prevAns=ans, returnDeps= T, ...) # first algorithmic options, taking the output of the previous run
    } else { # 0.2 < max conv < 0.5
      ans <- siena07(alg1, data=dat, effects=eff, prevAns=ans, returnDeps= T, ...) # second algorithmic option, taking output of previous
    }
  }
  if (tm > 0.25) # when stopped, and not converged:
  {
    cat(    "Warning: convergence inadequate.\n") # print warning
  }
  ans # final siena07 results
}
```

```{r}
analyseData <- function(i){
  cat(' class ',i,'* ') # show progress, which classroom
  sink('temp.txt') # unclutter screen
  mod <- makeData(i) # list with Sienadata, effects, 2 algorithms
  
  sink() # unclutter screen
  ModEstimates <- siena07ToConvergence(mod$algo0, mod$algo1,
                                      dat = mod$Data, eff = mod$Eff)
 
   # add a group number to the object:
  ModEstimates$groupNumber <- i
  ModEstimates # results
}
```

## SAOM - 1st round
```{r}
results1_1300 <- analyseData(1300) 
results1_1500 <- analyseData(1500) 
results1_3300 <- analyseData(3300) 
results1_6200 <- analyseData(6200)

# convergence for 4 classrooms
```

## SAOM - 2nd try
```{r}
# adapt the makeData function
makeData <- function(i){ # change: dolby = T, firstg = 0.02
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = T, seed=567, firstg = 0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678, firstg = 0.02 )
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results1_3100 <- analyseData(3100)
```

```{r}
# adapt the makeData function
makeData <- function(i){ # cond = F (unconditional estimation)
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = T, seed=567, cond=F)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678,cond=F )
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results1_3200 <- analyseData(3200) 
```

```{r}
# adapt the makeData function
makeData <- function(i){ #  fix transitive triplets
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, fix = T, test = T)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt)
   effects <- includeEffects(effects, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = F, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results1_3400 <- analyseData(3400)
```

```{r}
# save results in one list
resultslist1 <- list(results1_1300,results1_1500,results1_3100,results1_3200,results1_3300,results1_3400,results1_6200)
save(resultslist1,file='resultslist1.Rdata')
```

```{r}
# list with results from syntax above
#load("~/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/resultslist1.Rdata")
```

## convergence check

```{r}
# Check model convergence:
resultslist <- resultslist1
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```

## standard errors
```{r}
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
sapply(resultslist, function(x){length(x$theta)}) # same length of parameters?
sapply(resultslist, function(x){x$effects$effectName}) # name and order of effects per class?
```

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist # make copy
resultslistb[[4]]$theta<- resultslistb[[4]]$theta[3:11] # deselect rate effects for class with unconditional estimation
resultslistb[[4]]$se<- resultslistb[[4]]$se[3:11]
parameters <-  sapply(resultslistb, function(x){x$theta}) # get estimates
standers <- sapply(resultslistb, function(x){x$se}) # get standard errors
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

large SE: Rule of thumb > 5 (I change larger than 10) but large SE is normal for covariates with little variance (<0.1)
large SE's:
density - 3300: 18.10
reciprocity - 1300, 12.46 and 3100, 35.56, 6200: 13.72

```{r}
# save
model1_par1 <- round(parameters,2)
model1_se1 <- round(standers,2)
save(model1_par1, file="model1_par1.Rdata")
save(model1_se1, file="model1_se1.Rdata")
```

```{r}
# check small variance? #
(resultslist1[[5]]$sd)^2 <0.1
(resultslist1[[1]]$sd)^2 <0.1
(resultslist1[[3]]$sd)^2 <0.1 # yes for reciprocity 3100, does not need to be fixed
(resultslist1[[7]]$sd)^2 <0.1
```

## fix parameters that had large SE's

```{r}
# fix density for 3300
makeData <- function(i){ # setting: default, dolby = F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, density, fix = T, test=T) # fix
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results1_3300 <- analyseData(3300)
```


```{r}
# fix reciprocity for 3100
makeData <- function(i){ # setting: default, dolby = T
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, fix = T, test=T) # fix
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
results1_3100 <- analyseData(3100)
```

```{r}
# fix reciprocity for 6200
makeData <- function(i){ # setting: unconditional
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, fix = T, test=T) # fix
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  algo0 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), n3=5000, dolby = T, seed=567, firstg = 0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model1', i, sep=""), nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678, firstg=0.02)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
results1_6200 <- analyseData(6200)
```

```{r}
# add new simulation results to the list
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
resultslist1F <- resultslist1
resultslist1F[[1]] <- results1_1300
resultslist1F[[5]] <- results1_3300
resultslist1F[[7]] <- results1_6200
save(resultslist1F,file='resultslist1F.Rdata')
```

```{r}
# load results of the syntax above
load("~/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/resultslist1F.Rdata")
```

## Convergence check 2

```{r}
# Check convergence:
resultslist <- resultslist1F
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```
## control standard errors 2

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist # make copy
resultslistb[[4]]$theta<- resultslistb[[4]]$theta[3:11] # deselect rate effects for class 4
resultslistb[[4]]$se<- resultslistb[[4]]$se[3:11]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

```{r}
# save
model1_par1F <- round(parameters,2)
model1_se1F <- round(standers,2)
save(model1_par1F, file="model1_par1F.Rdata")
save(model1_se1F, file="model1_se1F.Rdata")
```

## Goodness of fit
```{r, message = FALSE}
# make function for Geodesic distribution
GeodesicDistribution <- function(i, data, sims, period, groupName,
	varName, levls = c(1:5,Inf), cumulative= TRUE, ...) {
    x <- networkExtraction(i, data, sims, period, groupName, varName)
    require(sna)
    a <- sna::geodist(symmetrize(x))$gdist
    if (cumulative)
    {
        gdi <- sapply(levls, function(i){ sum(a <= i) })
    }
    else
    {
        gdi <- sapply(levls, function(i){ sum(a == i) })
    }
    names(gdi) <- as.character(levls)
    return(gdi)
}
```  

```{r, message=FALSE}
# make a list of graphs and of the p-values of the gof estimatiioon
GOF <- list()
GOFP <- list()
for(i in 1:length(resultslist)){
  
print(i) # check progress
  
gof1.indegrees <- sienaGOF(resultslist[[i]],IndegreeDistribution,
                           varName = "emperors",cumulative = FALSE)
gof1.outdegrees <- sienaGOF(resultslist[[i]],OutdegreeDistribution,
	                            varName = "emperors",cumulative = FALSE)
gof1.triads <- sienaGOF(resultslist[[i]],TriadCensus,varName = "emperors")
gof1.geodesic <- sienaGOF(resultslist[[i]],GeodesicDistribution,
                           varName = "emperors",cumulative = FALSE)
# save p-values
P <- c(gof1.indegrees$Joint$p,
       gof1.outdegrees$Joint$p,
       gof1.triads$Joint$p,
       gof1.geodesic$Joint$p)

GOFP[[i]] <- P

goflist <- list(gof1.indegrees, gof1.outdegrees, gof1.triads, gof1.geodesic)
GOF[[i]] <- goflist
}
```

```{r}
# save
save(GOFP,file='GOFP1F.Rdata')
save(GOF,file='GOF1F.Rdata')
```

```{r}
# goodness of fit? control p is not <0.05
GOFP # fit outdegrees of 1300,3100,3300,6200 not great, but nowhere 0.
```

## table the results: estimates and significance

```{r, include = F}
results.table1 <- list()
for(i in 1:length(resultslist)){

parameter <- resultslist[[i]]$effects$effectName
type <- resultslist[[i]]$effects$type
estimate <- resultslist[[i]]$theta
st.error <- sqrt(diag(resultslist[[i]]$covtheta))
normal.variate <- estimate/st.error
p.value.2sided <- 2*pnorm(abs(normal.variate),lower.tail = FALSE)

results.table1[[i]] <- data.frame(parameter,
	                  estimate = round(estimate,3),
	                  st.error = round(st.error,3),
	                  normal.variate = round(normal.variate,2),
	                  p.value = round(p.value.2sided,4))
}
```

```{r}
# save the results
save(results.table1, file="results.table1.Rdata")
```
## meta-analysis
```{r}
# meta analysis for the results of the 7 classrooms
meta1 <-siena08(resultslist, projname= 'meta1', maxit = 200)
save(meta1, file='meta1.Rdata')
```

```{r}
#load('meta1.Rdata')
meta <- meta1
```

```{r}
# aree the SE's RANDOM?
plot(meta, which = 1:length(meta$theta),
                         useBound=TRUE, layout = c(2,2))
```

```{r}
# fishertest
neff <- sum(resultslist[[1]]$effects$include)
# Construct the names for the effects:
efnames <- names(meta)[1:neff]

Fishers <- t(sapply(1:neff,
                    function(i){c(meta[[i]]$cjplus, meta[[i]]$cjminus,
                                  meta[[i]]$cjplusp, meta[[i]]$cjminusp,
                                  2*meta[[i]]$n1 )}))
rownames(Fishers) <- efnames
colnames(Fishers) <- c('Fplus', 'Fminus', 'pplus', 'pminus', 'df')
df_Fishers<- as_tibble(round(Fishers,3),rownames = NA)

df_Fishersint <- df_Fishers %>% mutate('pos_sig'= ifelse(pplus <= 0.025, "yes","no"), 'neg_sig' = ifelse(pminus <= 0.025, "yes","no"))
rownames(df_Fishersint) <- efnames
kbl(df_Fishersint) %>% kable_styling()
```

```{r}
# meta-analysis of the mean
parameters.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$mu.ml,
                                                meta[[i]]$mu.ml.se, meta[[i]]$mu.confint,
                                                meta[[i]]$sigma.ml, meta[[i]]$sigma.confint,
                                                meta[[i]]$n1)}))

colnames(parameters.08) <- c('mu-hat', 'mu-se',
                             'mu-min', 'mu-plus', 'alpha_mu',
                             'sigma-hat', 'sigma-min', 'sigma-plus', 'alpha_sigma', 'N')
```


```{r}
# save 
save(Fishers, file = 'Fishers1.Rdata')
save(parameters.08,file = 'Meta.Par1.Rdata')
```

```{r}
# Extract heterogeneity tests from siena08 output;
# these are called Q in Snijders & Baerveldt (2003):
hetero.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Qstat,
                                            meta[[i]]$n1-1, meta[[i]]$pttilde)}))
colnames(hetero.08) <- c('Q', 'df', 'pQ')
# These are: Q statistic; degrees of freedom; p-value
rownames(hetero.08) <- efnames
round(hetero.08, 3)

# Extract overall tests;
Overalls.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Tsq,
                                              meta[[i]]$n1-1, meta[[i]]$pTsq)}))
colnames(Overalls.08) <- c('T^2', 'df', 'pT^2')

# These are: Q statistic; degrees of freedom; p-value
rownames(Overalls.08) <- efnames
round(Overalls.08, 3)

save(Overalls.08, file='overalls08.1.Rdata')
```