---
title: "'The Naked Emperor'- thesis syntax 4: Analysis Model 2 - SAOM MoM and meta-analysis"
subtitle: "Lisanne van Veen"
output: pdf_document
---
This script runs the second model (structural effects + gender effects+ intimidation mechanism) in R for Method of Moments for each class, followed by meta-analysis of the results.

Algorithmic parameters are adapted to each classroom for reaching convergence.
After a first round, effects with high standard errors are set to fixed values for more reliable estimates for other model effects.
Goodness of Fit is assessed for indegrees, outdegrees, triadic closure and geodesic distribution.

Beside the model specification and the adaptation of algorithmic parameters, the code is similar to thesis syntax 3: Analysis model 1.

## preliminaries

```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r, message = F}
library(RSiena)
library(tidyverse)
library(kableExtra)
```

## Functions
```{r}
makeData <- function(i){
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  
  #structural effects
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)

  # gender effects
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  
  # INTIMIDATION MECHANISM
  # H1a: relational aggression and perceived antisocial behavior precedes NE nomination
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational") # main effect of     relational aggression
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") # main effect of   perceived antisocial behavior

  # H1b: having more friends, and being perceived ass aggressive/antisocial lead to more NE nominations
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational")) # interaction for more friends and relational aggression
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial")) # interaction  for more friend antisocial behavior

  # H1c: perceived social attributes moderate the relation between relational aggression and NE nomination
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social") # main effect of perceived social behavior
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social")) # interaction effect of relational aggression and prosocial beh.
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social")) # interaction effect of anti-social and prosocial beh.

  # algorithms
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = T, seed=567)

  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678)
  
  # output is a list including the data, the effects, and two algorithms
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
siena07ToConvergence <- function(alg0, alg1, dat, eff, ans0=NULL, ...){
  numr <- 0 # count number of runs
  ans <- siena07(x = alg0, data=dat, effects=eff, prevAns=ans0,returnDeps= T, ...) # first run
  
  repeat { # code will be repeated until certain conditions are satisfied
    
    save(ans, file=paste("ans",numr,".RData",sep="")) # save first run results as R object 
    numr <- numr+1 # count number of repeated runs
    tm <- ans$tconv.max # maximum convergence indicator
    cat(numr, tm,"\n") # report progress
    
    # Stop if:
    if (tm < 0.20) {break} # run is successful
    if (tm > 10) {break}   # there is no hope for good estimates
    if (numr > 10) {break} # it takes too many runs for convergence
    
    # Continue if
    if (tm > 0.5){ # max convergence is above 0.5
      ans <- siena07(alg0, data=dat, effects=eff, prevAns=ans, returnDeps= T,...) # first algorithmic options
    } else { # 0.2 < max conv < 0.5
      ans <- siena07(alg1, data=dat, effects=eff, prevAns=ans, returnDeps= T,...) # second algorithmic options
    }
  }
  if (tm > 0.25) # when stopped, and not converged:
  {
    cat(    "Warning: convergence inadequate.\n") # print warning
  }
  ans # final siena07 results
}
```

```{r}
analyseData <- function(i){
  cat(' class ',i,'* ') # show progress, which classroom
  sink('temp.txt') # unclutter screen
  mod <- makeData(i) # list with Sienadata, effects, 2 algorithms
  
  sink() # unclutter screen
  ModEstimates <- siena07ToConvergence(mod$algo0, mod$algo1,
                                      dat = mod$Data, eff = mod$Eff)
 
   # add a group number to the object:
  ModEstimates$groupNumber <- i
  ModEstimates # results
}
```

## SAOM first round
```{r}
results2_1300 <- analyseData(1300) # converged
results2_1500 <- analyseData(1500) # converged
# only 2 classes converged
```

## SAOM - 2nd try
```{r}
# change makeData function
makeData <- function(i){ # change: firstg = 0.02
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational") 
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial")
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational")) 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial")) 
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = T, seed=567, firstg = 0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678, firstg = 0.02 )
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results2_3100 <- analyseData(3100) #converged
results2_6200 <- analyseData(6200) #converged
```

```{r}
makeData <- function(i){ # change: cond = F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial")
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = T, seed=567, cond = F)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678 ,cond=F)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results2_3200 <- analyseData(3200) # converged
```

```{r}
makeData <- function(i){ # change: dolby = F, firstg = 0.02, cond=F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial")
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational")) 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = F, seed=567,firstg = 0.02, cond = F)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678,firstg = 0.02, cond = F)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results2_3400 <- analyseData(3400) # converged
```

```{r}
makeData <- function(i){ # change: dolby = F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial")
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational")) 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = F, seed=565)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F,seed=564)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results2_3300 <- analyseData(3300)
```

```{r}
# save results in a list
resultslist2 <- list(results2_1300,results2_1500,results2_3100,results2_3200,results2_3300,results2_3400,results2_6200)
save(resultslist2,file='resultslist2.Rdata')
```


```{r}
# load results from syntax above
#load('resultslist2.Rdata')
```

## check convergence
```{r}
# Check convergence:
resultslist <- resultslist2
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```
## control standard errors

```{r}
groups <- sapply(resultslist, function(x){x$groupNumber}) # save group numbers
sapply(resultslist, function(x){length(x$effects$effectName)}) # how many effects for each class?
sapply(resultslist, function(x){x$effects$effectName}) # order?
```

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist
resultslistb[[4]]$theta<- resultslistb[[4]]$theta[3:21]
resultslistb[[4]]$se<- resultslistb[[4]]$se[3:21]
resultslistb[[6]]$theta<- resultslistb[[6]]$theta[3:21]
resultslistb[[6]]$se<- resultslistb[[6]]$se[3:21]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```
```{r}
# check small variance? if yes no fixing needed
(resultslist2[[1]]$sd)^2 <0.1# yes for recip 1300
(resultslist2[[3]]$sd)^2 <0.1# yes for recip 3100
(resultslist2[[5]]$sd)^2 <0.1# no
(resultslist2[[7]]$sd)^2 <0.1# yes for recip 6200
```

## fix parameters

```{r}
# 1300: relational, relational*social
makeData <- function(i){ # default
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational", fix=T,test=T)
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial")
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational")) 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social") 
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"), fix=T, test = T)
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social")) 
  
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = T, seed=567, firstg = 0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678, firstg = 0.02 )
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results2_1300 <- analyseData(1300)
```

```{r}
# 3300: density, gender, relational*social
makeData <- function(i){ # change: dolby=F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, density, fix=T, test=T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender", fix=T, test=T)
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial")
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational")) 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social") 
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"), fix=T, test = T)
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social")) 
  
  algo0 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""), n3=5000, dolby = F, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model2', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results2_3300 <- analyseData(3300)
```

```{r}
# save new results
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
resultslist2F <- resultslist2 # copy of previous SAOM
resultslist2F[[1]] <- results2_1300 # replace
resultslist2F[[5]] <- results2_3300 # replace
save(resultslist2F,file='resultslist2F.Rdata')
```

```{r}
# results of syntax above
#load("~/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/resultslist2F.Rdata")
```

## check convergence 2
```{r}
# Check convergence:
resultslist <- resultslist2F
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```
## check SE 2

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist
resultslistb[[4]]$theta<- resultslistb[[4]]$theta[3:21]
resultslistb[[4]]$se<- resultslistb[[4]]$se[3:21]
resultslistb[[6]]$theta<- resultslistb[[6]]$theta[3:21]
resultslistb[[6]]$se<- resultslistb[[6]]$se[3:21]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```
```{r}
# check small variance?
(resultslist2[[1]]$sd)^2 <0.1# yes for recip 1300
(resultslist2[[3]]$sd)^2 <0.1# yes for recip 3100
(resultslist2[[7]]$sd)^2 <0.1# yes for recip 6200
```

## Goodness of FIT
```{r, message = FALSE}
GeodesicDistribution <- function(i, data, sims, period, groupName,
	varName, levls = c(1:5,Inf), cumulative= TRUE, ...) {
    x <- networkExtraction(i, data, sims, period, groupName, varName)
    require(sna)
    a <- sna::geodist(symmetrize(x))$gdist
    if (cumulative)
    {
        gdi <- sapply(levls, function(i){ sum(a <= i) })
    }
    else
    {
        gdi <- sapply(levls, function(i){ sum(a == i) })
    }
    names(gdi) <- as.character(levls)
    return(gdi)
}
```  

```{r}
GOF <- list()
GOFP <- list()
for(i in 1:length(resultslist)){
  
print(i) # check progress
  
gof1.indegrees <- sienaGOF(resultslist[[i]],IndegreeDistribution,
                           varName = "emperors",cumulative = FALSE)
gof1.outdegrees <- sienaGOF(resultslist[[i]],OutdegreeDistribution,
	                            varName = "emperors",cumulative = FALSE)
gof1.triads <- sienaGOF(resultslist[[i]],TriadCensus,varName = "emperors")
gof1.geodesic <- sienaGOF(resultslist[[i]],GeodesicDistribution,
                           varName = "emperors",cumulative = FALSE)
# save p-values
P <- c(gof1.indegrees$Joint$p,
       gof1.outdegrees$Joint$p,
       gof1.triads$Joint$p,
       gof1.geodesic$Joint$p)

GOFP[[i]] <- P

goflist <- list(gof1.indegrees, gof1.outdegrees, gof1.triads, gof1.geodesic)
GOF[[i]] <- goflist
}
```

```{r}
save(GOFP,file='GOFP2F.Rdata')
save(GOF,file='GOF2F.Rdata')
```

```{r}
# GOF? p<0.05? 
GOFP # fit of outdegrees not great for 1300 and 3100
```

## table the results
```{r, include = F}
results.table2 <- list()
for(i in 1:length(resultslist)){

parameter <- resultslist[[i]]$effects$effectName
type <- resultslist[[i]]$effects$type
estimate <- resultslist[[i]]$theta
st.error <- sqrt(diag(resultslist[[i]]$covtheta))
normal.variate <- estimate/st.error
p.value.2sided <- 2*pnorm(abs(normal.variate),lower.tail = FALSE)

results.table2[[i]] <- data.frame(parameter,
	                  estimate = round(estimate,3),
	                  st.error = round(st.error,3),
	                  normal.variate = round(normal.variate,2),
	                  p.value = round(p.value.2sided,4))
}
```

```{r}
save(results.table2, file='results.table2.Rdata')
```

# meta-analysis
```{r}
meta2 <-siena08(resultslist, projname= 'meta2', maxit = 200)
save(meta2, file='meta2.Rdata')
```

```{r}
load('meta2.Rdata')
meta <- meta2
```

```{r}
# SE RANDOM?
plot(meta, which = 1:length(meta$theta),
                         useBound=TRUE, layout = c(2,2))
```

```{r}
# fishertest
neff <- sum(resultslist[[1]]$effects$include)
# Construct the names for the effects:
efnames <- names(meta)[1:neff]

# The first 7 letters are redundant and will be dropped:
efnames <- substring(efnames, 8)

Fishers <- t(sapply(1:neff,
                    function(i){c(meta[[i]]$cjplus, meta[[i]]$cjminus,
                                  meta[[i]]$cjplusp, meta[[i]]$cjminusp,
                                  2*meta[[i]]$n1 )}))
rownames(Fishers) <- efnames
colnames(Fishers) <- c('Fplus', 'Fminus', 'pplus', 'pminus', 'df')
df_Fishers<- as_tibble(round(Fishers,3),rownames = NA)

df_Fishersint <- df_Fishers %>% mutate('pos_sig'= ifelse(pplus <= 0.025, "yes","no"), 'neg_sig' = ifelse(pminus <= 0.025, "yes","no"))
rownames(df_Fishersint) <- efnames
kbl(df_Fishersint) %>% kable_styling()
```

```{r}
parameters.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$mu.ml,
                                                meta[[i]]$mu.ml.se, meta[[i]]$mu.confint,
                                                meta[[i]]$sigma.ml, meta[[i]]$sigma.confint,
                                                meta[[i]]$n1)}))

colnames(parameters.08) <- c('mu-hat', 'mu-se',
                             'mu-min', 'mu-plus', 'alpha_mu',
                             'sigma-hat', 'sigma-min', 'sigma-plus', 'alpha_sigma', 'N')
# These are: parameter estimate for population mean; s.e.;
# confidence interval for population mean (left, right, significance level);
# estimate for population standard deviation;
# confidence interval for standard deviation (left, right, significance level);
# number of groups on which this is based.
```

```{r}
save(Fishers, file = 'Fishers2.Rdata')
save(parameters.08, file = 'Meta.Par2.Rdata')
```

```{r}
# Extract heterogeneity tests from siena08 output;
# these are called Q in Snijders & Baerveldt (2003):
hetero.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Qstat,
                                            meta[[i]]$n1-1, meta[[i]]$pttilde)}))
colnames(hetero.08) <- c('Q', 'df', 'pQ')
# These are: Q statistic; degrees of freedom; p-value
rownames(hetero.08) <- efnames
round(hetero.08, 3)

# Extract overall tests;
Overalls.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Tsq,
                                              meta[[i]]$n1-1, meta[[i]]$pTsq)}))
colnames(Overalls.08) <- c('T^2', 'df', 'pT^2')

# These are: Q statistic; degrees of freedom; p-value
rownames(Overalls.08) <- efnames
round(Overalls.08, 3)

save(Overalls.08, file='overalls08.2.Rdata')
```
