---
title: "'The Naked Emperor'- thesis syntax 5: Analysis Model 3 - SAOM MoM and meta-analysis"
subtitle: "Lisanne van Veen"
output: pdf_document
---

This script runs the third model (structural effects + gender effects+ information mechanism) in R for Method of Moments for each class, followed by meta-analysis of the results.

Algorithmic parameters are adapted to each classroom for reaching convergence.
After a first round, effects with high standard errors are set to fixed values for more reliable estimates for other model effects.
Goodness of Fit is assessed for indegrees, outdegrees, triadic closure and geodesic distribution.

Beside the model specification and the adaptation of algorithmic parameters, the code is similar to thesis syntax 3: Analysis model 1.

## preliminaries

```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r}
library(RSiena)
library(kableExtra)
library(tidyverse)
```

## functions

```{r}
makeData <- function(i){#default
  
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  #structural effects
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  
  # gender effects
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  
  # INFORMATION mechanism
  # H2a: gossip precedes NE nomination
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  # H2b: a friendship tie leads to same NE nomination target (triadic closure, WWX, XWX)
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 

  # algorithms
  # for the first run, and repeated runs if necessary (after max convergence > 0.5)
  # n3=5000 for publication
  algo0 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""), n3=5000, dolby = T, seed=567)
  
  # for other repeated runs if necessary (after 0.2 < max conv. < 0.5)
 
   # n2start 2.52*(p+7) where p is number of parameters-conditional rate functions (Manual, p.79)
  # high value is double
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  
  algo1 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  
  # output is a list including the data, the effects, and two algorithms
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
siena07ToConvergence <- function(alg0, alg1, dat, eff, ans0=NULL, ...){
  numr <- 0 # count number of runs
  ans <- siena07(x = alg0, data=dat, effects=eff, prevAns=ans0,returnDeps= T, ...) # first run
  
  repeat { # code will be repeated until certain conditions are satisfied
    
    save(ans, file=paste("ans",numr,".RData",sep="")) # save first run results as R object 
    numr <- numr+1 # count number of repeated runs
    tm <- ans$tconv.max # maximum convergence indicator
    cat(numr, tm,"\n") # report progress
    
    # Stop if:
    if (tm < 0.20) {break} # run is successful
    if (tm > 10) {break}   # there is no hope for good estimates
    if (numr > 10) {break} # it takes too many runs for convergence
    
    # Continue if
    if (tm > 0.5){ # max convergence is above 0.5
      ans <- siena07(alg0, data=dat, effects=eff, prevAns=ans,returnDeps= T, ...) # first algorithmic options
    } else { # 0.2 < max conv < 0.5
      ans <- siena07(alg1, data=dat, effects=eff, prevAns=ans,returnDeps= T, ...) # second algorithmic optiions
    }
  }
  if (tm > 0.25) # when stopped, and not converged:
  {
    cat(    "Warning: convergence inadequate.\n") # print warning
  }
  ans # final siena07 results
}
```

```{r}
analyseData <- function(i){
  cat(' class ',i,'* ') # show progress, which classroom
  sink('temp.txt') # unclutter screen
  mod <- makeData(i) # list with Sienadata, effects, 2 algorithms
  
  sink() # unclutter screen
  ModEstimates <- siena07ToConvergence(mod$algo0, mod$algo1,
                                      dat = mod$Data, eff = mod$Eff)
 
   # add a group number to the object:
  ModEstimates$groupNumber <- i
  ModEstimates # results
}
```

## SAOM first round

```{r}
results3_1300 <- analyseData(1300) #conv
results3_3100 <- analyseData(3100) #conv
results3_3300 <- analyseData(3300) # conv
results3_6200 <- analyseData(6200) # conv
```

## SAOM second try
```{r}
makeData <- function(i){ # change = firstg = 0.02
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  algo0 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""), n3=5000, dolby = T, seed=567, firstg=0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678, firstg=0.02)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results3_1500 <- analyseData(1500) # conv
results3_3200 <- analyseData(3200) #conv
```

```{r}
makeData <- function(i){ # change = dolby=F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, fix = T, test = T)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  algo0 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results3_3400 <- analyseData(3400)
```

```{r}
resultslist3 <- list(results3_1300,results3_1500,results3_3100,results3_3200,results3_3300,results3_3400,results3_6200)
save(resultslist3,file='resultslist3.Rdata')
```

```{r}
# results from syntax aboove
#load('resultslist3.Rdata')
```

## check convergence
```{r}
# Check convergence:
resultslist <- resultslist3
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```
```{r}
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
sapply(resultslist, function(x){length(x$theta)}) # same length of parameters?
```

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist # make copy
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

```{r}
# save se's
model3_par1 <- round(parameters,2)
model3_se1 <- round(standers,2)
# save
save(model3_par1, file="model3_par1.Rdata")
save(model3_se1, file="model3_se1.Rdata")
```

```{r}
# check small variance? # no
(resultslist[[1]]$sd)^2 <0.1
(resultslist[[5]]$sd)^2 <0.1
(resultslist[[7]]$sd)^2 <0.1 
# recip 1300, recip 6200, outdegree + gossiptarget 3300.
```

## fix parameters

```{r}
#1300 reciprocity
makeData <- function(i){#default
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, fix = T, test = T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  algo0 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results3_1300 <- analyseData(1300)
results3_6200 <- analyseData(6200)
```

```{r}
# 3300 gossiptarget
makeData <- function(i){#default
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, density, fix = T, test = T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1= "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget", fix = T, test = T)
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  algo0 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model3', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results3_3300 <- analyseData(3300)
```

```{r}
# save new results 
resultslist3F <- resultslist3 # copy
resultslist3F[[1]] <- results3_1300 # overwrite
resultslist3F[[5]] <- results3_3300
resultslist3F[[7]] <- results3_6200
save(resultslist3F,file='resultslist3F.Rdata')
```

```{r}
# results of syntax above
#load("~/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/resultslist3F.Rdata")
```

## check convergence 2

```{r}
# Check convergence:
resultslist <- resultslist3F
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist # make copy
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

## Goodness of fit
```{r, message = FALSE}
GeodesicDistribution <- function(i, data, sims, period, groupName,
	varName, levls = c(1:5,Inf), cumulative= TRUE, ...) {
    x <- networkExtraction(i, data, sims, period, groupName, varName)
    require(sna)
    a <- sna::geodist(symmetrize(x))$gdist
    if (cumulative)
    {
        gdi <- sapply(levls, function(i){ sum(a <= i) })
    }
    else
    {
        gdi <- sapply(levls, function(i){ sum(a == i) })
    }
    names(gdi) <- as.character(levls)
    return(gdi)
}
```  

```{r}
GOF <- list()
GOFP <- list()
for(i in 1:length(resultslist3)){
  
print(i) # check progress
  
gof1.indegrees <- sienaGOF(resultslist[[i]],IndegreeDistribution,
                           varName = "emperors",cumulative = FALSE)
gof1.outdegrees <- sienaGOF(resultslist[[i]],OutdegreeDistribution,
	                            varName = "emperors",cumulative = FALSE)
gof1.triads <- sienaGOF(resultslist[[i]],TriadCensus,varName = "emperors")
gof1.geodesic <- sienaGOF(resultslist[[i]],GeodesicDistribution,
                           varName = "emperors",cumulative = FALSE)
# save p-values
P <- c(gof1.indegrees$Joint$p,
       gof1.outdegrees$Joint$p,
       gof1.triads$Joint$p,
       gof1.geodesic$Joint$p)

GOFP[[i]] <- P

goflist <- list(gof1.indegrees, gof1.outdegrees, gof1.triads, gof1.geodesic)
GOF[[i]] <- goflist
}
```

```{r}
save(GOFP,file='GOFP3F.Rdata')
save(GOF,file='GOF3F.Rdata')
```

```{r}
# p<0.05?
GOFP #outdegree problematic (1300,3100,3200,3300)
```

## table the results
```{r, include = F}
results.table3 <- list()
for(i in 1:length(resultslist)){

parameter <- resultslist[[i]]$effects$effectName
type <- resultslist[[i]]$effects$type
estimate <- resultslist[[i]]$theta
st.error <- sqrt(diag(resultslist[[i]]$covtheta))
normal.variate <- estimate/st.error
p.value.2sided <- 2*pnorm(abs(normal.variate),lower.tail = FALSE)

results.table3[[i]] <- data.frame(parameter,
	                  estimate = round(estimate,3),
	                  st.error = round(st.error,3),
	                  normal.variate = round(normal.variate,2),
	                  p.value = round(p.value.2sided,4))
}
```

```{r}
save(results.table3, file='results.table3.Rdata')
```

## meta-analysis

```{r}
meta3 <-siena08(resultslist, projname= 'meta3', maxit = 200)
save(meta3, file='meta3.Rdata')
```

```{r}
load('meta3.Rdata')
meta <- meta3
```

```{r}
# SE RANDOM?
plot(meta, which = 1:length(meta$theta),
                         useBound=TRUE, layout = c(2,2))
```

```{r}
# fishertest
neff <- sum(resultslist[[1]]$effects$include)
# Construct the names for the effects:
efnames <- names(meta)[1:neff]
# The first 7 letters are redundant and will be dropped:
efnames <- substring(efnames, 8)

Fishers <- t(sapply(1:neff,
                    function(i){c(meta[[i]]$cjplus, meta[[i]]$cjminus,
                                  meta[[i]]$cjplusp, meta[[i]]$cjminusp,
                                  2*meta[[i]]$n1 )}))
rownames(Fishers) <- efnames
colnames(Fishers) <- c('Fplus', 'Fminus', 'pplus', 'pminus', 'df')
df_Fishers<- as_tibble(round(Fishers,3),rownames = NA)

df_Fishersint <- df_Fishers %>% mutate('pos_sig'= ifelse(pplus <= 0.025, "yes","no"), 'neg_sig' = ifelse(pminus <= 0.025, "yes","no"))
rownames(df_Fishersint) <- efnames
kbl(df_Fishersint) %>% kable_styling()
```

```{r}
parameters.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$mu.ml,
                                                meta[[i]]$mu.ml.se, meta[[i]]$mu.confint,
                                                meta[[i]]$sigma.ml, meta[[i]]$sigma.confint,
                                                meta[[i]]$n1)}))

colnames(parameters.08) <- c('mu-hat', 'mu-se',
                             'mu-min', 'mu-plus', 'alpha_mu',
                             'sigma-hat', 'sigma-min', 'sigma-plus', 'alpha_sigma', 'N')
```

```{r}
save(Fishers, file = 'Fishers3.Rdata')
save(parameters.08, file = 'Meta.Par3.Rdata')
```


```{r}
# Extract heterogeneity tests from siena08 output;
# these are called Q in Snijders & Baerveldt (2003):
hetero.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Qstat,
                                            meta[[i]]$n1-1, meta[[i]]$pttilde)}))
colnames(hetero.08) <- c('Q', 'df', 'pQ')
# These are: Q statistic; degrees of freedom; p-value
rownames(hetero.08) <- efnames
round(hetero.08, 3)

# Extract overall tests;
Overalls.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Tsq,
                                              meta[[i]]$n1-1, meta[[i]]$pTsq)}))
colnames(Overalls.08) <- c('T^2', 'df', 'pT^2')
# These are: Q statistic; degrees of freedom; p-value
rownames(Overalls.08) <- efnames
round(Overalls.08, 3)

save(Overalls.08, file='overalls08.3.Rdata')
```
