---
title: "'The Naked Emperor'- thesis syntax 6: Analysis Model 4 - SAOM MoM and meta-analysis"
subtitle: "Lisanne van Veen"
output: pdf_document
---

This script runs the fourth model (structural effects + gender effects + antipathy) in R for Method of Moments for each class, followed by meta-analysis of the results.

Algorithmic parameters are adapted to each classroom for reaching convergence.
After a first round, effects with high standard errors are set to fixed values for more reliable estimates for other model effects.
Goodness of Fit is assessed for indegrees, outdegrees, triadic closure and geodesic distribution.

Beside the model specification and the adaptation of algorithmic parameters, the code is similar to thesis syntax 3: Analysis model 1.

## preliminaries

```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r}
library(RSiena)
library(tidyverse)
library(kableExtra)
```

## functions

```{r}
makeData <- function(i){ # default settings
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, name = 'emperors')
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt, name= 'emperors')
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
siena07ToConvergence <- function(alg0, alg1, dat, eff, ans0=NULL, ...){
  numr <- 0 # count number of runs
  ans <- siena07(x = alg0, data=dat, effects=eff, prevAns=ans0,returnDeps= T, ...) # first run
  repeat { # code will be repeated until certain conditions are satisfied
    save(ans, file=paste("ans",numr,".RData",sep="")) # save first run results as R object 
    numr <- numr+1 # count number of repeated runs
    tm <- ans$tconv.max # maximum convergence indicator
    cat(numr, tm,"\n") # report progress
    # Stop if:
    if (tm < 0.20) {break} # run is successful
    if (tm > 10) {break}   # there is no hope for good estimates
    if (numr > 10) {break} # it takes too many runs for convergenc
    # Continue if
    if (tm > 0.5){ # max convergence is above 0.5
      ans <- siena07(alg0, data=dat, effects=eff, prevAns=ans,returnDeps= T, ...) 
    } else { # 0.2 < max conv < 0.5
      ans <- siena07(alg1, data=dat, effects=eff, prevAns=ans,returnDeps= T, ...)
    }
  }
  if (tm > 0.25) # when stopped, and not converged:
  {
    cat(    "Warning: convergence inadequate.\n") # print warning
  }
  ans # final siena07 results
}
```

```{r}
analyseData <- function(i){
  cat(' class ',i,'* ') # show progress, which classroom
  sink('temp.txt') # unclutter screen
  mod <- makeData(i) # list with Sienadata, effects, 2 algorithms
  sink() # unclutter screen
  ModEstimates <- siena07ToConvergence(mod$algo0, mod$algo1,
                                      dat = mod$Data, eff = mod$Eff)
  # add a group number to the object:
  ModEstimates$groupNumber <- i
  ModEstimates # results
}
```

## SAOM first try

```{r}
results4_1300 <- analyseData(1300) # converged
results4_3300 <- analyseData(3300) #converged
```

## SAOM second try

```{r}
makeData <- function(i){ #firstg = 0.02
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, name = 'emperors')
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt, name= 'emperors')
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""), n3=5000, dolby = T, seed=567,firstg = 0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F, seed=5678,firstg = 0.02)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results4_1500 <- analyseData(1500) # conv
results4_3100 <- analyseData(3100) #conv
results4_6200 <- analyseData(6200) #converged
```

```{r}
makeData <- function(i){ #firstg=0.02, cond = F
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, name = 'emperors')
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt, name= 'emperors')
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""), n3=5000, dolby = T, seed=567,firstg = 0.02, cond= F)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F, seed=5678,firstg = 0.02, cond = F)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results4_3200 <- analyseData(3200)
```

```{r}
makeData <- function(i){ #transTrip = fixed
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, name = 'emperors', fix = T, test = T)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt, name= 'emperors')
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results4_3400 <- analyseData(3400) #conv
```
```{r}
resultslist4 <- list(results4_1300, results4_1500,results4_3100, results4_3200, results4_3300, results4_3400,results4_6200)
save(resultslist4,file='resultslist4.Rdata')
```

```{r}
# results of syntax above
#load("~/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/resultslist4.Rdata")
resultslist4
```

## check convergence

```{r}
# Check convergence:
resultslist <- resultslist4
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```
## check Standard Errors

```{r}
groups <- sapply(resultslist, function(x){x$groupNumber})
sapply(resultslist, function(x){length(x$theta)}) # same length of parameters?
```

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist
resultslistb[[4]]$theta<- resultslistb[[4]]$theta[-c(1,2)]
resultslistb[[4]]$se<- resultslistb[[4]]$se[-c(1,2)]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

```{r}
# save se's
model4_par1 <- round(parameters,2)
model4_se1 <- round(standers,2)
# save
save(model4_par1, file="model4_par1.Rdata")
save(model4_se1, file="model4_se1.Rdata")
```

```{r}
# check small variance? #
(resultslist[[1]]$sd)^2 <0.1
(resultslist[[3]]$sd)^2 <0.1 # recip 3100
(resultslist[[5]]$sd)^2 <0.1
(resultslist[[7]]$sd)^2 <0.1 # recip 6200
# to fix: reciprocity 1300, density 3300
```
## fix parameters
```{r}
# fix SE for high density 3300
makeData <- function(i){
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, density, name = 'emperors', fix = T, test = T)
  effects <- includeEffects(effects, transTrip, name = 'emperors')
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt, name= 'emperors')
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results4_3300 <- analyseData(3300)
```

```{r}
# high SE recip
makeData <- function(i){
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, name = 'emperors', fix = T, test = T)
  effects <- includeEffects(effects, transTrip, name = 'emperors')
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt, name= 'emperors')
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""), n3=5000, dolby = T, seed=567)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model4', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T, seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results4_1300 <- analyseData(1300)
```

```{r}
# save new results 
resultslist4F <- resultslist4 # copy
resultslist4F[[1]] <- results4_1300 # overwrite
resultslist4F[[5]] <- results4_3300
save(resultslist4F,file='resultslist4F.Rdata')
```

```{r}
# load results from syntax above
load("~/Desktop/Master Computational Social Science/NETWORK PAPER/Naked Emperors/resultslist4F.Rdata")
```


## Check convergence 2

```{r}
# Check convergence:
resultslist <- resultslist4F
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```

## check standard errors 2

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist
resultslistb[[4]]$theta<- resultslistb[[4]]$theta[-c(1,2)]
resultslistb[[4]]$se<- resultslistb[[4]]$se[-c(1,2)]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

## Goodness of FIT

```{r, message = FALSE}
GeodesicDistribution <- function(i, data, sims, period, groupName,
	varName, levls = c(1:5,Inf), cumulative= TRUE, ...) {
    x <- networkExtraction(i, data, sims, period, groupName, varName)
    require(sna)
    a <- sna::geodist(symmetrize(x))$gdist
    if (cumulative)
    {
        gdi <- sapply(levls, function(i){ sum(a <= i) })
    }
    else
    {
        gdi <- sapply(levls, function(i){ sum(a == i) })
    }
    names(gdi) <- as.character(levls)
    return(gdi)
}
```  

```{r}
GOF <- list()
GOFP <- list()
for(i in 1:length(resultslist)){
  
print(i) # check progress
  
gof1.indegrees <- sienaGOF(resultslist[[i]],IndegreeDistribution,
                           varName = "emperors",cumulative = FALSE)
gof1.outdegrees <- sienaGOF(resultslist[[i]],OutdegreeDistribution,
	                            varName = "emperors",cumulative = FALSE)
gof1.triads <- sienaGOF(resultslist[[i]],TriadCensus,varName = "emperors")
gof1.geodesic <- sienaGOF(resultslist[[i]],GeodesicDistribution,
                           varName = "emperors",cumulative = FALSE)
# save p-values
P <- c(gof1.indegrees$Joint$p,
       gof1.outdegrees$Joint$p,
       gof1.triads$Joint$p,
       gof1.geodesic$Joint$p)

GOFP[[i]] <- P

goflist <- list(gof1.indegrees, gof1.outdegrees, gof1.triads, gof1.geodesic)
GOF[[i]] <- goflist
}
```

```{r}
save(GOFP,file='GOFP4F.Rdata')
save(GOF,file='GOF4F.Rdata')
```

```{r}
#load(GOFP4F.Rdata)
#load(GOF4F.Rdata)
```

```{r}
#GOF p, should not be below p<0.05 (as a rule of thumb)
GOFP
# outdegrees for 1300, 3100, 3300
```

## table the results

```{r, include = F}
results.table4 <- list()
for(i in 1:length(resultslist)){

parameter <- resultslist[[i]]$effects$effectName
type <- resultslist[[i]]$effects$type
estimate <- resultslist[[i]]$theta
st.error <- sqrt(diag(resultslist[[i]]$covtheta))
normal.variate <- estimate/st.error
p.value.2sided <- 2*pnorm(abs(normal.variate),lower.tail = FALSE)

results.table4[[i]] <- data.frame(parameter,
	                  estimate = round(estimate,3),
	                  st.error = round(st.error,3),
	                  normal.variate = round(normal.variate,2),
	                  p.value = round(p.value.2sided,4))
}
```

```{r}
save(results.table4, file='results.table4.Rdata')
```

# meta-analysis

```{r}
meta4 <-siena08(resultslist, projname= 'meta4', maxit = 200)
save(meta4, file='meta4.Rdata')
```

```{r}
#load('meta4.Rdata')
meta <- meta4
```

```{r}
# SE RANDOM?
plot(meta, which = 1:length(meta$theta),
                         useBound=TRUE, layout = c(2,2))
```

```{r}
# fishertest
neff <- sum(resultslist[[1]]$effects$include)
# Construct the names for the effects:
efnames <- names(meta)[1:neff]
# The first 7 letters are redundant and will be dropped:

Fishers <- t(sapply(1:neff,
                    function(i){c(meta[[i]]$cjplus, meta[[i]]$cjminus,
                                  meta[[i]]$cjplusp, meta[[i]]$cjminusp,
                                  2*meta[[i]]$n1 )}))
rownames(Fishers) <- efnames
colnames(Fishers) <- c('Fplus', 'Fminus', 'pplus', 'pminus', 'df')
df_Fishers<- as_tibble(round(Fishers,3),rownames = NA)

df_Fishersint <- df_Fishers %>% mutate('pos_sig'= ifelse(pplus <= 0.025, "yes","no"), 'neg_sig' = ifelse(pminus <= 0.025, "yes","no"))
rownames(df_Fishersint) <- efnames
kbl(df_Fishersint) %>% kable_styling()
```

```{r}
parameters.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$mu.ml,
                                                meta[[i]]$mu.ml.se, meta[[i]]$mu.confint,
                                                meta[[i]]$sigma.ml, meta[[i]]$sigma.confint,
                                                meta[[i]]$n1)}))

colnames(parameters.08) <- c('mu-hat', 'mu-se',
                             'mu-min', 'mu-plus', 'alpha_mu',
                             'sigma-hat', 'sigma-min', 'sigma-plus', 'alpha_sigma', 'N')
```

```{r}
save(Fishers, file = 'Fishers4.Rdata')
save(parameters.08,file = 'Meta.Par4.Rdata')
```


```{r}
# Extract heterogeneity tests from siena08 output;
# these are called Q in Snijders & Baerveldt (2003):
hetero.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Qstat,
                                            meta[[i]]$n1-1, meta[[i]]$pttilde)}))
colnames(hetero.08) <- c('Q', 'df', 'pQ')
# These are: Q statistic; degrees of freedom; p-value
rownames(hetero.08) <- efnames
round(hetero.08, 3)

# Extract overall tests;
Overalls.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Tsq,
                                              meta[[i]]$n1-1, meta[[i]]$pTsq)}))
colnames(Overalls.08) <- c('T^2', 'df', 'pT^2')
# These are: Q statistic; degrees of freedom; p-value
rownames(Overalls.08) <- efnames
round(Overalls.08, 3)

save(Overalls.08, file='overalls08.4.Rdata')
```



