---
title: "'The Naked Emperor'- thesis syntax 7: Analysis Model5 - SAOM MoM and meta-analysis"
subtitle: "Lisanne van Veen"
output: pdf_document
---

This script runs the fifth model (Full model) in R for Method of Moments for each class, followed by meta-analysis of the results.

Algorithmic parameters are adapted to each classroom for reaching convergence.
After a first round, effects with high standard errors are set to fixed values for more reliable estimates for other model effects.
Goodness of Fit is assessed for indegrees, outdegrees, triadic closure and geodesic distribution.

Beside the model specification and the adaptation of algorithmic parameters, the code is similar to thesis syntax 3: Analysis model 1.


## preliminaries

```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r, message = F}
library(RSiena) # basic Rsiena package
library(kableExtra)
library(tidyverse)
```

## functions
```{r}
makeData <- function(i){
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  
  effects <- getEffects(dataset)
  #structural effects
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  
  # INTIMIDATION MECHANISM
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 

  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))

  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))

  # INFORMATION mechanism
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  
  # antipathy
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  
  # algorithms
  algo0 <- sienaAlgorithmCreate(projname = paste('model5', i, sep=""), n3=5000, dolby = T, seed=5672)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678)
  
  # output is a list including the data, the effects, and two algorithms
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```


```{r}
# Utility function: variation of a siena07 function,
# For repeated runs of siena07 until convergence is reached or deemed unfeasible
siena07ToConvergence <- function(alg0, alg1, dat, eff, ans0=NULL, ...){
  numr <- 0 # count number of runs
  ans <- siena07(x = alg0, data=dat, effects=eff, prevAns=ans0, returnDeps= T,...) # first run
  
  repeat { # code will be repeated until certain conditions are satisfied
    save(ans, file=paste("ans",numr,".RData",sep="")) # save first run results as R object 
    numr <- numr+1 # count number of repeated runs
    tm <- ans$tconv.max # maximum convergence indicator
    cat(numr, tm,"\n") # report progress
    
    # Stop if:
    if (tm < 0.20) {break} # run is successful
    if (tm > 10) {break}   # there is no hope for good estimates
    if (numr > 10) {break} # it takes too many runs for convergence
    
    # Continue if
    if (tm > 0.5){ # max convergence is above 0.5
      ans <- siena07(alg0, data=dat, effects=eff, prevAns=ans,returnDeps= T, ...) # first algorithmic options
    } else { # 0.2 < max conv < 0.5
      ans <- siena07(alg1, data=dat, effects=eff, prevAns=ans,returnDeps= T, ...) # second algorithmic optiions
    }
  }
  if (tm > 0.25) # when stopped, and not converged:
  {
    cat(    "Warning: convergence inadequate.\n") # print warning
  }
  ans # final siena07 results
}
```

```{r}
analyseData <- function(i){
  cat(' class ',i,'* ') # show progress, which classroom
  sink('temp.txt') # unclutter screen
  mod <- makeData(i) # list with Sienadata, effects, 2 algorithms
  
  sink() # unclutter screen
  ModEstimates <- siena07ToConvergence(mod$algo0, mod$algo1,
                                      dat = mod$Data, eff = mod$Eff)
 
   # add a group number to the object:
  ModEstimates$groupNumber <- i
  ModEstimates # results
}
```

## SAOM first try

```{r}
results5_1300 <- analyseData(1300) 
results5_1500 <- analyseData(1500)
results5_3100 <- analyseData(3100)
results5_3400 <- analyseData(3400) 
```

## SAOM second try

```{r}
makeData <- function(i){ #dolby = F
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = F, seed=5672)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results5_3200 <- analyseData(3200)
results5_6200 <- analyseData(6200) 
```

```{r}
makeData <- function(i){ #firstg = 0.02, cond=F
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = T, seed=5672, firstg = 0.02, cond = F)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678, firstg = 0.02, cond = F)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
```

```{r}
results5_3300 <- analyseData(3300)
```

```{r}
resultslist5 <- list(results5_1300,results5_1500,results5_3100,results5_3200,results5_3300, results5_3400, results5_6200)
save(resultslist5,file='resultslist5.Rdata')
```

```{r}
#load('resultslist5.Rdata')
```

## check convergence

```{r}
resultslist <- resultslist5
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```
```{r}
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
sapply(resultslist, function(x){length(x$theta)}) # same length of parameters?
```

## check standard errors

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist # make copy
resultslistb[[5]]$theta<- resultslistb[[5]]$theta[-c(1,2)] 
resultslistb[[5]]$se<- resultslistb[[5]]$se[-c(1,2)]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

```{r}
# save se's
model5_par1 <- round(parameters,2)
model5_se1 <- round(standers,2)
# save
save(model5_par1, file="model5_par1.Rdata")
save(model5_se1, file="model5_se1.Rdata")
```

```{r}
# check small variance? #
(resultslist[[1]]$sd)^2 <0.1
(resultslist[[3]]$sd)^2 <0.1
(resultslist[[5]]$sd)^2 <0.1 # gossiptarget 3300
(resultslist[[6]]$sd)^2 <0.1
(resultslist[[7]]$sd)^2 <0.1 

# to fix:
#1300: recip, relational, relational*social
# 3100 recip
# 3300: density, relational, gender, relational*social
# 3400: trans triplets
# 6200: recip
```

## fix parameters

```{r}
#1300: recip, relational
makeData <- function(i){
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, fix = T, test = T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational", fix = T, test = T)
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = F, seed=5672)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results5_1300 <- analyseData(1300)
```

```{r}
# 3100 recip
makeData <- function(i){
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, fix = T, test = T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = F, seed=5672)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}
results5_3100 <- analyseData(3100)
```

```{r}
# 3300: density, relational, gender
makeData <- function(i){ #firstg = 0.02, cond=F
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
 effects <- includeEffects(effects, density, fix = T, test = T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender", fix = T, test = T)
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational", fix = T, test = T)
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = T, seed=5672, firstg = 0.02, cond = F)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678, firstg = 0.02, cond = F)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results5_3300 <- analyseData(3300)
```

```{r}
# 3400: trans triplets
makeData <- function(i){
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, transTrip, fix = T, test = T)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = T, seed=5672)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = T,seed=5678)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results5_3400 <- analyseData(3400)
```

```{r}
# 6200: recip
makeData <- function(i){ #dolby = F, firstg=0.02
  #load data
  load(paste0('netDynamics',i,'.Rdata'))
  dataset <- netDynamics
  effects <- getEffects(dataset)
  effects <- includeEffects(effects, recip, fix = T, test = T)
  effects <- includeEffects(effects, transTrip)
  effects <- includeEffects(effects, inPopSqrt, outActSqrt, outPopSqrt)
  effects <- includeEffects(effects, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="relational")
  effects <- includeEffects(effects, name = "emperors",X, interaction1="antisocial") 
  effects <- includeEffects(effects, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  effects <- includeInteraction(effects, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="social")
  effects <- includeInteraction(effects, name = "emperors",X,X, interaction1=c("relational", "social"))
  effects <- includeInteraction(effects, name = "emperors", X, X, interaction1 = c("antisocial", "social"))
  effects <- includeEffects(effects, name = "emperors",X, interaction1="gossiptarget")
  effects <- includeEffects(effects, name = "emperors", WXX, XWX, interaction1="friends") 
  effects <- includeEffects(effects, name = "emperors", X, interaction1 = "antipathy")
  algo0 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""), n3=5000, dolby = F, seed=5672, firstg = 0.02)
  p <- length(effects$effectName)
  n2s <- ((2.52)*(p+7))*2
  n2s <- round(n2s)
  algo1 <- sienaAlgorithmCreate(projname = paste('model5alt', i, sep=""),
                                nsub=1, n2start = n2s, n3=5000, dolby = F,seed=5678, firstg=0.02)
  list(Data=dataset, Eff=effects , algo0=algo0, algo1=algo1)
}

results5_6200 <- analyseData(6200)
```

```{r}
# to fix:
# 1300: recip, relational, relational*social
# 3100 recip
# 3300: density, relational, gender, relational*social
# 3400: trans triplets
# 6200: recip
# add new simulation results to the list
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
resultslist5F <- resultslist5
resultslist5F[[1]] <- results5_1300
resultslist5F[[3]] <- results5_3100
resultslist5F[[5]] <- results5_3300
resultslist5F[[6]] <- results5_3400
resultslist5F[[7]] <- results5_6200
save(resultslist5F,file='resultslist5F.Rdata')
```
```{r}
#load('resultslist5F.Rdata')
```


## check convergence 2

```{r}
resultslist <- resultslist5F
hist(sapply(resultslist, function(x){x$tconv.max}), xlab='tconv.max', main='')
max(sapply(resultslist, function(x){x$tconv.max})) 
```

```{r}
(groups <- sapply(resultslist, function(x){x$groupNumber})) # models for which classrooms?
sapply(resultslist, function(x){length(x$theta)}) # same length of parameters?
```

## check standard errors 2

```{r}
# Extract parameter estimates and standard errors
resultslistb <- resultslist # make copy
resultslistb[[5]]$theta<- resultslistb[[5]]$theta[-c(1,2)] 
resultslistb[[5]]$se<- resultslistb[[5]]$se[-c(1,2)]
parameters <-  sapply(resultslistb, function(x){x$theta})
standers <- sapply(resultslistb, function(x){x$se})
eff.names <-
    resultslist[[1]]$effects[resultslist[[1]]$effects$include,'effectName']
rownames(parameters) <- eff.names
rownames(standers) <- eff.names
colnames(parameters) <- sapply(resultslist, function(x){x$groupNumber})
colnames(standers) <- sapply(resultslist, function(x){x$groupNumber})
# print rounded to 2 decimals so that on a wide console everything can fit.
#round(parameters,2)
round(standers,2)
```

```{r}
# save se's
model5_par2 <- round(parameters,2)
model5_se2 <- round(standers,2)
# save
save(model5_par2, file="model5_par2.Rdata")
save(model5_se2, file="model5_se2.Rdata")
```

## table results

```{r}
# table the results
results.table5 <- list()
for(i in 1:length(resultslist)){

parameter <- resultslist[[i]]$effects$effectName
type <- resultslist[[i]]$effects$type
estimate <- resultslist[[i]]$theta
st.error <- sqrt(diag(resultslist[[i]]$covtheta))
normal.variate <- estimate/st.error
p.value.2sided <- 2*pnorm(abs(normal.variate),lower.tail = FALSE)

results.table5[[i]] <- data.frame(parameter,
	                  estimate = round(estimate,3),
	                  st.error = round(st.error,3),
	                  normal.variate = round(normal.variate,2),
	                  p.value = round(p.value.2sided,4))
}
```

```{r}
results.table5
save(results.table5, file = 'results.table5.Rdata')
```

## Goodness of FIT

```{r, message = FALSE}
GeodesicDistribution <- function(i, data, sims, period, groupName,
	varName, levls = c(1:5,Inf), cumulative= TRUE, ...) {
    x <- networkExtraction(i, data, sims, period, groupName, varName)
    require(sna)
    a <- sna::geodist(symmetrize(x))$gdist
    if (cumulative)
    {
        gdi <- sapply(levls, function(i){ sum(a <= i) })
    }
    else
    {
        gdi <- sapply(levls, function(i){ sum(a == i) })
    }
    names(gdi) <- as.character(levls)
    return(gdi)
}
```  

```{r}
GOF <- list()
GOFP <- list()
for(i in 1:length(resultslist)){
  
print(i) # check progress
  
gof1.indegrees <- sienaGOF(resultslist[[i]],IndegreeDistribution,
                           varName = "emperors",cumulative = FALSE)
gof1.outdegrees <- sienaGOF(resultslist[[i]],OutdegreeDistribution,
	                            varName = "emperors",cumulative = FALSE)
gof1.triads <- sienaGOF(resultslist[[i]],TriadCensus,varName = "emperors")
gof1.geodesic <- sienaGOF(resultslist[[i]],GeodesicDistribution,
                           varName = "emperors",cumulative = FALSE)
# save p-values
P <- c(gof1.indegrees$Joint$p,
       gof1.outdegrees$Joint$p,
       gof1.triads$Joint$p,
       gof1.geodesic$Joint$p)

GOFP[[i]] <- P

goflist <- list(gof1.indegrees, gof1.outdegrees, gof1.triads, gof1.geodesic)
GOF[[i]] <- goflist
}
```


```{r}
save(GOFP,file='GOFP5F.Rdata')
save(GOF,file='GOF5F.Rdata')
```

```{r}
GOFP # only outdegrees of class 1300 and 3100
```

## META ANALYSIS

```{r}
meta5 <- siena08(resultslist, projname="meta5")
save(meta5, file = 'meta5.Rdata')
```

```{r}
meta <- meta5
```

```{r}
# SE RANDOM?
plot(meta, which = 1:length(meta$theta),
                         useBound=TRUE, layout = c(2,2))
```

```{r}
# fishertest
neff <- sum(resultslist[[1]]$effects$include)
# Construct the names for the effects:
efnames <- names(meta)[1:neff]
# The first 7 letters are redundant and will be dropped:
efnames <- substring(efnames, 8)

Fishers <- t(sapply(1:neff,
                    function(i){c(meta[[i]]$cjplus, meta[[i]]$cjminus,
                                  meta[[i]]$cjplusp, meta[[i]]$cjminusp,
                                  2*meta[[i]]$n1 )}))
rownames(Fishers) <- efnames
colnames(Fishers) <- c('Fplus', 'Fminus', 'pplus', 'pminus', 'df')
df_Fishers<- as_tibble(round(Fishers,3),rownames = NA)

df_Fishersint <- df_Fishers %>% mutate('pos_sig'= ifelse(pplus <= 0.025, "yes","no"), 'neg_sig' = ifelse(pminus <= 0.025, "yes","no"))
rownames(df_Fishersint) <- efnames
kbl(df_Fishersint) %>% kable_styling()
```

```{r}
parameters.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$mu.ml,
                                                meta[[i]]$mu.ml.se, meta[[i]]$mu.confint,
                                                meta[[i]]$sigma.ml, meta[[i]]$sigma.confint,
                                                meta[[i]]$n1)}))

colnames(parameters.08) <- c('mu-hat', 'mu-se',
                             'mu-min', 'mu-plus', 'alpha_mu',
                             'sigma-hat', 'sigma-min', 'sigma-plus', 'alpha_sigma', 'N')
```

```{r}
save(Fishers, file = 'Fishers5.Rdata')
save(parameters.08,file = 'Meta.Par5.Rdata')
```

```{r}
# Extract heterogeneity tests from siena08 output;
# these are called Q in Snijders & Baerveldt (2003):
hetero.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Qstat,
                                            meta[[i]]$n1-1, meta[[i]]$pttilde)}))
colnames(hetero.08) <- c('Q', 'df', 'pQ')
# These are: Q statistic; degrees of freedom; p-value
rownames(hetero.08) <- efnames
round(hetero.08, 3)

# Extract overall tests;
Overalls.08 <- t(sapply(1:neff, function(i){c(meta[[i]]$Tsq,
                                              meta[[i]]$n1-1, meta[[i]]$pTsq)}))
colnames(Overalls.08) <- c('T^2', 'df', 'pT^2')
# These are: Q statistic; degrees of freedom; p-value
rownames(Overalls.08) <- efnames

round(Overalls.08, 3)
save(Overalls.08, file='overalls08.5.Rdata')
```

