---
title: "'The Naked Emperor'- thesis syntax 8: Analysis Full model - Bayesian multilevel Random Coefficients"
subtitle: "Lisanne van Veen"
output: pdf_document
---

This script shows the analysis by Bayesian multilevel random coefficients with RSiena, as well as the generating of the plots. 

Plots used functions sourced from the relevant script from the RSiena website, as shown in syntax 9. 

## preliminaries

```{r}
knitr::opts_chunk$set(eval=F) #prevent evaluation while knitting pdf to show syntax
```

```{r}
# load libraries
library(RSiena)
library(multiSiena)
library(parallel)
```

## preperation for heterogeneity test
```{r}
# select groups for analysis
groups <- c(1300,1500,3100,3200,3300,3400,6200,7100)

# create list with data objects per group
l <- paste0('netDynamics',groups,'.Rdata')
objectlist <- list()
t <- 0
for(i in l){
  t <- t+1
  load(i)
  objectlist[[t]] <- netDynamics
}

# create multigroup object
(multigroup <- sienaGroupCreate(objectlist))

# load multigroup siena Fit object
#load("multigroup_SienaFit.Rdata")
GEff <- getEffects(multigroup)
# effectsDocumentation(GEff)

# Model specification for multilevel MoM to use for timetest, without interaction effects:
# structural effects
  GEff<- includeEffects(GEff, transTrip)
  GEff<- includeEffects(GEff, inPopSqrt, outActSqrt, outPopSqrt)
  
# gender effects
  GEff<- includeEffects(GEff, name = "emperors", altX, egoX, sameX, interaction1 = "Gender")
  
  # INTIMIDATION mechanism
  GEff<- includeEffects(GEff, name = "emperors",X, interaction1="relational")
  GEff<- includeEffects(GEff, name = "emperors",X, interaction1="antisocial") 
  GEff<- includeEffects(GEff, name = "emperors", altX,egoX,simX,interaction1="nfriends") 
  GEff<- includeEffects(GEff, name = "emperors",X, interaction1="social")

  # INFORMATION mechanism
  GEff<- includeEffects(GEff, name = "emperors",X, interaction1="gossiptarget")
  GEff<- includeEffects(GEff, name = "emperors", WXX, XWX, interaction1="friends") 
  
  # CONTROL: antipathy
  GEff<- includeEffects(GEff, name = "emperors", X, interaction1 = "antipathy")
```

```{r}
# create algorithm
Galgo <- sienaAlgorithmCreate(projname = 'GCBG', seed = 5678, cond=T)

# detect for use of multiple cores during run
n.clus <- detectCores() - 1 #7

# run multilevel MoM, for timetest
(Gans.timetest <- siena07(Galgo, data=multigroup, effects=GEff,
            useCluster=TRUE, nbrNodes=n.clus))

save(Gans.timetest, GEff, file='Gans.timetest.RData')

# siena timetest for heterogeneity of parameters
# to help to decide which parameters should be random
# look at non-significant effects and high chi^2 values of effect-wise joint significance tests
timetest <- sienaTimeTest(Gans.timetest)
save(timetest, file = 'timetest.Rdata')
summary(timetest)
# high chi-squared ~ >60 for
# density, indegree pop(sqrt), outdegree pop (sqrt), outdegree act(sqrt), closure of friends WXX XWX, nfriends ego and similarity, all gender effects, antipathy.
```

## modeling for BMRC

```{r}
# include interactions in model specification for multigroup analysis (first siena07, then Bayesian estimation)
  GEff<- includeInteraction(GEff, name = "emperors",altX,X, interaction1 = c("nfriends","relational"))
  GEff<- includeInteraction(GEff, name = "emperors",altX,X, interaction1 = c("nfriends","antisocial"))
  GEff<- includeInteraction(GEff, name = "emperors",X,X, interaction1=c("relational", "social"))
  GEff<- includeInteraction(GEff, name = "emperors", X, X, interaction1 = c("antisocial", "social"))

# specify random effects (not sign, or chi-squared ~> 60) (density is default)
  GEff<- setEffect(GEff, inPopSqrt, random = TRUE)
  GEff<- setEffect(GEff, outActSqrt, random = TRUE)
  GEff<- setEffect(GEff, name = "emperors", altX,interaction1 = "Gender", random = TRUE)
  GEff<- setEffect(GEff, name = "emperors", egoX,interaction1 = "Gender", random = TRUE) 
  GEff<- setEffect(GEff, name = "emperors", sameX,interaction1 = "Gender", random = TRUE) 
  GEff<- setEffect(GEff, name = "emperors", egoX,interaction1="nfriends", random = TRUE) 
  GEff<- setEffect(GEff, name = "emperors", XWX, interaction1="friends", random = TRUE) 

# show effects list
print(GEff, includeRandoms=TRUE, dropRates=F)
```

## prior specifications

```{r}
#  define prior Mu and variance
GEff[(GEff$randomEffects | (GEff$basicRate & (GEff$group==1) )) & GEff$include, ]

# recommended: negative value for density, other means based on prior knowledge, covariates for research question 0, homophily controls 0.3-0.5
Mu <- rep(0,10)
Mu[3] <- -2  #  outdegree density
Mu[4] <- 0.2 #  indegree pop sqrt
Mu[5] <- 0.1 # outdegree act sqrt
Mu[10]<- 0.3 #  same gender


# prior variance
Sig <- matrix(0,10,10)
diag(Sig) <- 0.01 # reflects differences that may exist between different groups
```

```{r}
# Algorithm for prevAns SienaBayes
# Ripley (2021) p.119 -> MoM, nsub=2, firstg =< 0.05, cond = F (see help page)
# check for convergence and high estimates of non-rate parameters
Galg1 <- sienaAlgorithmCreate(projname = 'GCBG1', seed = 5678, n3 = 3000, nsub = 2, firstg=0.05, cond = F, dolby = T)

# Run twice
(Gans <- siena07(Galg1, data=multigroup, effects=GEff, useCluster=TRUE, nbrNodes=n.clus)) 
(Gans <- siena07(Galg1, data=multigroup, effects=GEff, useCluster=TRUE, nbrNodes=n.clus, prevAns = Gans)) 

save(Gans, file= 'Gans.Bayes.Rdata')
# load('Gans.Bayes.Rdata')

# non-rate parameters high? NO
# convergence for all non-rate parameters, however max conv ratio remains quite high: 0.86
Gans
```

## test run
```{r}
# algorithm for SienaBayes
GroupsAlgo <- sienaAlgorithmCreate(projname = 'Bayes_5', seed = 5678)

# initial test run
tryrun <- sienaBayes(data= multigroup, effects = GEff, algo = GroupsAlgo,
                           priorMu = Mu, priorSigma = Sig,
                           priorKappa = 0.01,
                           prevAns = Gans,
                           nwarm=5, nmain=10, nrunMHBatches=5, nImproveMH=20,
                           nbrNodes=n.clus, silentstart=FALSE, initgainGroupwise = 0.001)

save(tryrun, 'sBayes_test.Rdata')
#load('sBayes_test.Rdata')
summary(tryrun)
# high rate parameters for some groups? change intigainGroupwise
```

## BMRC
```{r}
# Complete Run
 Bayes5_2 <- sienaBayes(data= multigroup, effects = GEff, algo = GroupsAlgo,
                           initgainGlobal=0.1, initgainGroupwise = 0.001,
                           priorMu = Mu, priorSigma = Sig,
                           priorKappa = 0.01,
                           prevAns = Gans,
                           nwarm=500, nmain=2000, nrunMHBatches=40, nImproveMH=100,
                           nbrNodes=7, silentstart=FALSE) 

 save(Bayes5_2, file="groupBayes5_02.RData")
# load("groupBayes5_02.RData")
summary(Bayes5_2)
# check non stationarity:
NonRateTracePlots(Bayes5_2)
# no non-stationarity, longer run necesarry
```

```{r}
# Prolonging
 Bayes5_2ec <- sienaBayes(algo=GroupsAlgo, data = multigroup, effects = GEff,
                         initgainGlobal=0.1, initgainGroupwise = 0.001,
                         priorMu = Mu, priorSigma = Sig,
                         priorKappa = 0.01, 
                         prevBayes = Bayes5_2, 
                         nwarm = 500, nmain=2000, nrunMHBatches=40, nImproveMH=100,
                         nbrNodes=7, silentstart = FALSE)

save(Bayes5_2ec, file = "groupBayes5_2ec.RData")
```

```{r}
#combine
groupsBB <- glueBayes(Bayes5_2, Bayes5_2ec)
```

# Plotting and results
## traceplots

```{r}
# Make first plots
NonRateTracePlots(groupsBB, setOfEffects = 3:8, title = "NRTP_structEF")
NonRateTracePlots(groupsBB, setOfEffects = c(9:11,16:18,22:25), title = "NRTP_intim")
NonRateTracePlots(groupsBB, setOfEffects = c(12:14,15,19:21), title = "NRTP_inf_gen_dis")
RateTracePlots(groupsBB)
# non stationarity?
# starts to stabilize around 3000, but still quite spread
```

## results

```{r}
summary(groupsBB, nfirst = 3000) # select moment where convergence started to improve
```

```{r}
# parameters plots
getNames(groupsBB)
GlobalNonRateParameterPlots(groupsBB, setOfEffects = 3, title="gnet_density")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(4,5,6,7,8), title="gnet_network")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(9,22,24), title="gnet_relational")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(10,23,25), title="gnet_antisocial")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(11,16,17,18), title="gnet_social_nfriends")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(19,20,21), title="gnet_gender")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(12,13,14), title="gnet_gossip")
GlobalNonRateParameterPlots(groupsBB, setOfEffects = c(15), title="gnet_antipaty")
```

```{r}
shortBayesResults(groupsBB, nfirst = 3000)
```

```{r}
nrow(sGtest)
length(post.mean)
posterior.mean <- post.mean[17:39]
sGtest<-simpleBayesTest(groupsBB, nfirst=3000, ndigits = 3)
sGtest<-sGtest %>% mutate(`mu/eta` = posterior.mean) %>% rename(parameter = " ", cred.to = "  cred.to", `p (> 0)` = "  p  ")
sGtest <- sGtest %>% select(parameter, varying,`mu/eta`, cred.from,cred.to,`p (> 0)`)
```

```{r}
# Make table for output
ordered <- c(1,2,3,4,5,6,17,18,19,7,8,14,15,16,20,21,9,22,23,10,11,12,13)
sGtestor<-sGtest[ordered,]
rownames(sGtestor) <- NULL

sGtestor %>% kbl(caption="Table 8: Posterior Results of Bayesian Multilevel Random Coefficients", booktabs = T) %>%  kable_styling(font_size = 12, htmltable_class = "lightable-classic",html_font = "Times New Roman", full_width = F)  %>% pack_rows(group_label = "Structural effects", 1,6) %>% pack_rows("Gender effects", 7,9) %>% pack_rows("H1: Intimidation Mechanism", 10,20) %>% 
pack_rows("H2: Information Mechanism", 20,22) %>% 
pack_rows("antipathy", 23,23) %>% footnote(general="Source: RECENS(2016), N = 211")%>% save_kable(file="Bayesianresults.png",bs_theme = "flatly")
```

## density plots

```{r}
# distribution plots
AllDensityPlots(groupsBB, nfirst = 3000)
```

## MDS

```{r}
plotPostMeansMDS(groupsBB, excludeRates=F, nfirst = 3000, pmonly = 1, method = 3)
```

## global parameters
```{r}
GlobalRateParameterPlots(groupsBB)
GlobalNonRateParameterPlots(groupsBB, setOfEffects = 2, title="gnet_density")
GlobalNonRateParameterPlots(gans.e, setOfEffects = 3, title="gnet_recip")
GlobalNonRateParameterPlots(gans.e, setOfEffects = 4:8, title="gnet_struct")
GlobalNonRateParameterPlots(gans.e, setOfEffects = c(9,15,16), title="gnet_cov")
GlobalNonRateParameterPlots(gans.e, setOfEffects = 10:14, title="gnet_del")
GlobalNonRateParameterPlots(gans.e, setOfEffects = 17:21, title="gdel")
```



